Methodology for Assessing the State of the Practice for Domain X

### 2020-05-14 StateOfPractice/Methodology/Methodology.tex
added one question to task criteria
Some additions to the methodology

Purpose and scope of the document.  \wss{Needs to be filled in.  Should
	reference the overall research proposal, and the ``state of the practice''
	exercise in particular.}

@@

\begin{enumerate}
\item Identify domain.  (Provide criteria on a candidate domain.)
\item 
\end{enumerate}

\section{Identify Candidate Software}

@@

Commonality analysis.  Follow as for mesh generator (likely with less detail).

Commonality analysis document Steps:
\begin{enumerate}
	\item Introduction
	\item Overview of Domain
	\item Add Commonalities - Split into simulation, input, output, and nonfunctional requirements
	\item Add Variabilites - Split into simulation, input, output, system constraints, and nonfunctional requirements
	\item Add Parameters of Variation - Split into simulation, input, output, system constraints, and nonfunctional requirements
	\item Add Terminology, Definitions, Acronyms
\end{enumerate}

@@

\subsection{Task definition/selection criteria}
\begin {enumerate}
\item Tasks based on difficulty levels (Difficult, Medium and easy)
\item Commonly performed tasks (applicable to all the selected software)
\item Task that would/should generate errors messages or error codes
\item Tasks to check standards and conventions
\item Tasks that should provide users with the system's current state and what actions can be done or where to go or what change was made
\item Tasks related to what users will do in the real world
\item End to End tasks that require users to go through sequential or hierarchical steps.
\item Tasks that allow users to reuse a previously defined value without having to memorize or jot it.
\item Tasks that should provide users with feedback
\item Tasks that allow users to customize and use shortcuts, bookmarks, command keys etc.
\item Tasks to verify if the system is capable of preventing and /or reversing errors
\item Tasks that might lead the user to use help or documentation

>>>>

Purpose and scope of the document.  \wss{Needs to be filled in.  Should
	reference the overall research proposal, and the ``state of the practice''
	exercise in particular.  Reference questions we are trying to answer.}

\section{Research Questions}

In general questions:

\begin{enumerate}
\item Comparison between domains
\item How to measure qualities
\item How does the quality compare for projects with the most resources to those
  with the fewest?
\item What skills/knowledge are needed by future developers?
\item How can the development process be improved?
\item What are the common pain points?
\end{enumerate}

For each domain questions''

\begin{enumerate}
\item Best examples within the domain
\item What software artifacts?
\item What are the pain points?
\item Any advice on what can be done about the pain points?
\end{enumerate}

Measure the effort invested and the reward.  Related to sustainability.

Collect the data and see what conclusions follow.  For an individual domain,
between domains.  The process isn't so much about ranking the software as it is
about looking at the software closely and see what conclusions arise.  The
measurements are intended to force scrutiny, from different perspectives.

@@

\begin{enumerate}
\item Start with state of practice research questions.
\item Identify domain.  (Provide criteria on a candidate domain.)
\item Identify list of candidate software in the domain.  (Section~\ref{SecIdentifyCandSoft})
\item \emph{Domain Expert}: Vet domain software list.  
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})
\item \emph{Domain Expert}: Vet domain analysis
\item Measure using ``shallow'' measurement template.
\item Empirical measures.
\item Use AHP process to rank the software.  Tool for estimating AHP results?
  Tool for ranking and sorting by various criteria?  Conditional formula to
  assess software within each measure, or just use opinion of measurer?
\item Identify short list for deeper exploration.
\item \emph{Domain Expert}: vet AHP ranking and short list.
\item With short list:
\begin{enumerate}
\item Survey developers
\item Usability experiments
\item Performance benchmarks
\item Maintainability experiments
\end{enumerate}
\item Compare shallow and deep measures and ranking
\item Answers for research questions.
\end{enumerate}

\wss{The domain expert is involved in multiple steps in the process.  How best
  to get their feedback?  The domain experts are busy and are unlikely to devote
  significant time to the project.  We need to quickly get to the point.  Maybe
  something around task based inspection?  Directed interview?}

\section{Identify Candidate Software} \label{SecIdentifyCandSoft}

@@

Commonality analysis.  Follow as for mesh generator (likely with less detail).
Final result will be tables of commonalities, variabilities and parameters of
variation.

Commonality analysis document Steps:
\begin{enumerate}
\item Introduction
\item Overview of Domain
\item Add Commonalities - Split into simulation, input, output, and
  nonfunctional requirements
\item Add Variabilities - Split into simulation, input, output, system
  constraints, and nonfunctional requirements
\item Add Parameters of Variation - Split into simulation, input, output, system
  constraints, and nonfunctional requirements
\item Add Terminology, Definitions, Acronyms
\end{enumerate}

@@

\subsection{Task definition/selection criteria}
\begin {enumerate}
\item Tasks based on difficulty levels (Difficult, Medium and easy)
\item Commonly performed tasks (applicable to all the selected software)
\item Task that would/should generate errors messages or error codes
\item Tasks to check standards and conventions
\item Tasks that should provide users with the system's current state and what actions can be done or where to go or what change was made
\item Tasks related to what users will do in the real world
\item End to End tasks that require users to go through sequential or hierarchical steps.
\item Tasks that allow users to reuse a previously defined value without having to memorize or jot it.
\item Tasks that should provide users with feedback
\item Tasks that allow users to customize and use shortcuts, bookmarks, command keys etc.
\item Tasks to verify if the system is capable of preventing and /or reversing errors
\item Tasks that might lead the user to use help or documentation
\item Task to modify the source code
